Neural Neural Textures Make Sim2Real Consistent

### 2022-06-23 CORL/example.tex
Updates from Overleaf

\usepackage[final]{corl_2022} % Use this for the initial submission.
% \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{array, booktabs, ragged2e}
\usepackage{comment}

@@

% \title{TRITON: Globally Consistent Sim-to-Real Transfer
\title{\mbox{TRITON: Neural Neural Textures for Better Sim2Real}
%``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
%via Neural Textures
}

\author{%
	Ryan Burgert, Jinghuan Shang, Xiang Li, Michael S. Ryoo\\
	Department of Computer Science\\
	Stony Brook University\\
	Stony Brook, NY 11794 \\
	\texttt{\{rburgert,mryoo\}@cs.stonybrook.edu} \\
	% \And
	% Michael Ryoo \\
	% Department of Computer Science\\
	% Stony Brook University\\
	% Stony Brook, NY 11794 \\
	% \texttt{mryoo@cs.stonybrook.edu} \\
	%\And
%	Emma Burgert \\
%	Ryan Burgert's Dog\\
}

@@

\vspace{-8pt}
\paragraph{Neural Textures}
\citet{deferred_neural_rendering} introduced the concept of neural textures and image translators in the context of a deferred rendering pipeline, used in other works such as \cite{surgical_video_translation} which is closely related to our project. 
\citet{surgical_video_translation} differs from TRITON in a few very important aspects though, the biggest being that it only synthesizes new camera views, where the only difference between each scene is the placement of the camera. In contrast, our algorithm takes in scenes where several objects are placed in different places or deformed, so that one static  global 3d model of the environment is not sufficient to accomplish our tasks. In addition, TRITON uses a new type of neural texture called a ``neural neural texture'', which is represented continuously using a fourier feature network, as described in \citep{fourier_feature_networks}.

@@

%\subsection{Qualitative Evaluation Results}
%We show qualitative evaluation results ....[TODO]
\begin{figure}[th]
	\begin{center}
		\includegraphics[width=.9\textwidth]{../images/frame_inconsistency.pdf}
	\end{center}
	\vspace{-7pt}
	% Each outline color corresponds to the same cube.
	% The same cubes are marked with the same colored outlines across all photos.
	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
	\caption{
	    Comparison of image translation methods.
	    The first column is the UVL map as the input.
	    The other columns are results using different image translation methods.
		Each row of images shows a different random placement of objects in the scene.
		TRITON consistently outputs high quality results over different object arrangements. 
		``TRITON texture only'' stands for TRITON without two surface consistency losses $\lUC$ and $\lTR$.
		% Each column of images is a different image translation algorithm.
		% The same cube is marked with the same color outline across all photos.
		% TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
		% Meanwhile, CycleGAN for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
		% Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
		% CUT and CycleGAN are not consistent, while TRITON is.
		% TODO: Update the images in this to have the latest training iteration...
		}
		\vspace{-15pt}
		\label{fig:frame_inconsistency_diagram}
	\end{figure}

@@

\textbf{Task} We use a robot pose imitation task for our experiments. Given the input of a photo of real robot pose, the policy outputs robot controls to replicate that target pose. We measure the angular error between the replicated and target poses as our evaluation metric:$\sqrt{\sum_{j} (\hat{a}_j - a_j)^2}$,
where $\hat{a}_j$ and $a_j$ are replicated and target joint angles respectively, and $j$ is the joint index. We use an xArm robot which has 7 joints. We also attached patterns and tapes on the robot to make its texture more challenging to model.

>>>>

\usepackage[preprint]{corl_2022} % Use this for the initial submission.
% \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{array, booktabs, ragged2e}
\usepackage{comment}

@@

% \title{TRITON: Globally Consistent Sim-to-Real Transfer
\title{Neural Neural Textures Make Sim2Real Consistent}
% \title{Neural Texture Fields from Unpaired Images for Better? Realistic? Sim2Real}
%``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
%via Neural Textures

\author{%
	Ryan Burgert, Jinghuan Shang, Xiang Li, Michael S. Ryoo\\
	Department of Computer Science\\
	Stony Brook University\\
	Stony Brook, NY 11794 \\
	\texttt{\{rburgert,jishang, xiangli8, mryoo\}@cs.stonybrook.edu} \\
	% \And
	% Michael Ryoo \\
	% Department of Computer Science\\
	% Stony Brook University\\
	% Stony Brook, NY 11794 \\
	% \texttt{mryoo@cs.stonybrook.edu} \\
	%\And
%	Emma Burgert \\
%	Ryan Burgert's Dog\\
}

@@

\vspace{-8pt}
\paragraph{Neural Textures}
\citet{deferred_neural_rendering} introduced the concept of neural textures and image translators in the context of a deferred rendering pipeline, used in other works such as \cite{surgical_video_translation} which is closely related to our project. 
\citet{surgical_video_translation} differs from TRITON in a few very important aspects though, the biggest being that it only synthesizes new camera views, where the only difference between each scene is the placement of the camera. In contrast, our algorithm takes in scenes where several objects are placed in different places or deformed, so that one static  global 3d model of the environment is not sufficient to accomplish our tasks. In addition, TRITON uses a new type of neural texture called a ``neural neural texture'', which is represented continuously using a fourier feature network, as described in \citet{fourier_feature_networks}.

@@

%\subsection{Qualitative Evaluation Results}
%We show qualitative evaluation results ....[TODO]
\begin{figure}[th]
	\begin{center}
		\includegraphics[width=.9\textwidth]{../images/frame_inconsistency_diagram.png}
	\end{center}
	\vspace{-7pt}
	% Each outline color corresponds to the same cube.
	% The same cubes are marked with the same colored outlines across all photos.
	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
	\caption{
	    Comparison of image translation methods.
	    The first column is the UVL map as the input.
	    The other columns are results using different image translation methods.
		Each row of images shows a different random placement of objects in the scene.
		TRITON consistently outputs high quality results over different object arrangements. 
		``TRITON texture only'' stands for TRITON without two surface consistency losses $\lUC$ and $\lTR$.
		% Each column of images is a different image translation algorithm.
		% The same cube is marked with the same color outline across all photos.
		% TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
		% Meanwhile, CycleGAN for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
		% Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
		% CUT and CycleGAN are not consistent, while TRITON is.
		% TODO: Update the images in this to have the latest training iteration...
		}
		\vspace{-15pt}
		\label{fig:frame_inconsistency_diagram}
	\end{figure}

@@

\textbf{Task} We use a robot pose imitation task for our experiments. Given the input of a photo of real robot pose, the policy outputs robot controls to replicate that target pose. We measure the angular error between the replicated and target poses as our evaluation metric:$\sqrt{\sum_{j} (\hat{a}_j - a_j)^2}$,
where $\hat{a}_j$ and $a_j$ are replicated and target joint angles respectively, and $j$ is the joint index. We use an xArm robot which has seven joints. We also attached patterns and tapes on the robot to make its texture more challenging to model.
